Bye Hugo Academic, hello Distill for Rmarkdown

### 2022-01-30 _posts/2021-09-29-nomorehugo/nomorehugo.Rmd
publish acronyms post

---
title: "Bye Hugo Academic, hello Distill for Rmarkdown"
description: |
  Why I gave up on Hugo Academic
author:
  - name: Sam Parsons
    url: 
date: 09-29-2021
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Bye Hugo Academic, hello Distill for Rmarkdown"
description: |
  Why I gave up on Hugo Academic
date: 09-29-2021
output:
  distill::distill_article:
    self_contained: false
---
